Detailed disease progression of 88 patients hospitalized with Covid-19 in the Czech Republic: A dataset and exploratory analysis

### 2020-09-13 manuscript/manuscript.Rmd
Bit of writing

`brms` package [@http://zotero.org/users/5567156/items/7ER3ZSER]. The parametrization of the HMM is inspired by [@http://zotero.org/users/5567156/items/F9K2L5Q8] where an underlying continous process with given rates only between the neighbouring state and the transition matrix across all states is then computed as the total probability of transition across all possible paths.

>>>>

Second class of models are Bayesian hidden Markov models of disease progression implemented via a custom extension to the `brms` package [@http://zotero.org/users/5567156/items/7ER3ZSER]. The parametrization of the HMM is inspired by [@http://zotero.org/users/5567156/items/F9K2L5Q8] where an underlying continous process with given rates only between the neighbouring state and the transition matrix across all states is then computed as the total probability of transition across all possible paths. This class of models does not satisfy the proportional hazards assumption, instead, it is assumed the process has the Markov property - i.e. that the unobserved state and the covariates at a given day contain all the information to determine probabilities of the states on the next day.
